Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2012-05-29 Multiresolution_framework/ltx/manuscript.tex
edits to discussion about second order synaptic kernel

Additional extension for future work include extending the model to capture a second order synaptic response kernel. The second-order postsynaptic kernel proposed in \citet{VanRotterdam1982} leads to dynamics that are more reminiscent to real postsynaptic potentials. Another extension of this framework is the inclusion of finite distant-dependent action potential propagation velocity into the parametric neural field equations. \vik{In small networks the resulting delays via propagation can be neglected. However, delays must be accounted for in large scale networks. For instance, \citet{Ghosh2008} demonstrated that inclusion of time delays arising from propagation along connecting fibres are essential for the understanding of the fluctuations in resting state networks (see \citet{Deco2010} for review). In fact, \citet{Ghosh2008} emphasize that the couplings in large-scale brain networks have a space-time structure composed of their anatomical connectivity (space) and signal transmission delays (time). To capture correctly the constraints posed upon the network dynamics by connectivity, the space-time structure of the brain connectivity must be correctly estimated.} Finally, future work should be directed towards applying and validating the framework on real data.

>>>>

Additional extension for future work include extending the model to capture a second order synaptic response kernel. The second-order postsynaptic kernel proposed in \citet{VanRotterdam1982} leads to dynamics that are more reminiscent to real postsynaptic potentials ( see \citet{Spiegler2010,Spiegler2011} for example). Another extension of this framework is the inclusion of finite distant-dependent action potential propagation velocity into the parametric neural field equations. \vik{In small networks the resulting delays via propagation can be neglected. However, delays must be accounted for in large scale networks. For instance, \citet{Ghosh2008} demonstrated that inclusion of time delays arising from propagation along connecting fibres are essential for the understanding of the fluctuations in resting state networks (see \citet{Deco2010} for review). In fact, \citet{Ghosh2008} emphasize that the couplings in large-scale brain networks have a space-time structure composed of their anatomical connectivity (space) and signal transmission delays (time). To capture correctly the constraints posed upon the network dynamics by connectivity, the space-time structure of the brain connectivity must be correctly estimated.} Finally, future work should be directed towards applying and validating the framework on real data.
